MsCcHSFeed Outline

### 2022-01-07 MsCcHSFeedOutlineDec15.Rmd
Added code for binomial comparisons of death rates and WOWE/WE rates

>>>>

# Additional analyses

## Binomial of deaths between NP and P groups

```{r}
binomdeath <- datadead %>%
  select(ID, food, para, survived)

binomdeath$survived <- gsub("yes", 1, binomdeath$survived)
binomdeath$survived <- gsub("no", 0, binomdeath$survived)

binomdeath$survived <- as.numeric(binomdeath$survived)
```

### Run stats

```{r}
death <- glm(survived ~ food*para, data = binomdeath, family = "binomial")

summary(death)
```

```{r}
death2 <- glm(survived ~ para, data = binomdeath, family = "binomial")

summary(death2)
```

## Binomial of WOWE mongo outcomes

```{r}
binomWOWE <- data %>%
  select(ID, food, fate)

binomWOWE$fate <- gsub("wowe mongo", 1, binomWOWE$fate)
binomWOWE$fate <- gsub("wowe", 0, binomWOWE$fate)
binomWOWE$fate <- gsub("em", 0, binomWOWE$fate)
binomWOWE$fate <- gsub("wander", 0, binomWOWE$fate)

binomWOWE$fate <- as.numeric(binomWOWE$fate)
```

### Run stats

```{r}
wowe <- glm(fate ~ food, data = binomWOWE, family = "binomial")

summary(wowe)
```

## Binomial of WE outcomes

```{r}
binomWE <- data %>%
  select(ID, food, fate)

binomWE$fate <- gsub("wowe mongo", 0, binomWE$fate)
binomWE$fate <- gsub("wowe", 0, binomWE$fate)
binomWE$fate <- gsub("em", 1, binomWE$fate)
binomWE$fate <- gsub("wander", 0, binomWE$fate)

binomWE$fate <- as.numeric(binomWE$fate)
```

```{r}
we <- glm(fate ~ food, data = binomWE, family = "binomial")

summary(we)
```
